Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
edit

A more complete understading of the influence of baryons on the
different properties we have measure will certainly require to study
how the halo and the disc co-evolved as a function of time and a
calibrating the effect of the cosmic web (both dark matter and
gaseous)  \citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
We finalize by suggesting that twisting shells in the density is a
feature that deserves to be explored in the process of constraining
shape parameters from tidal stream data.  The inclusion of a
parameterization describing this degree of twisting might relax the
conflict between the observational constraints and the numerical
results.

>>>>

A more complete understading of the influence of baryons on the
different properties we have measured will require two elements, at
least. First, an study on how the halo and the disc co-evolved as a
function of time. Second, a calibrating the effect of the cosmic web
(both dark matter and gaseous) on any evoluionary trend
\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} 
We finalize by suggesting that the twisting density shells we find in
some of the halos is feature that deserves to be explored in the
process of constraining shape parameters from tidal stream data.  The
inclusion of a parameterization describing this degree of twisting
might relax the conflict between the observational constraints and the
numerical results.
